\section{Philosophy and Scope Statement}

MIFX --- Machining Intent Format eXchange --- is a minimal, open specification 
for the structured representation and exchange of machining intent in a portable, 
durable, and implementation-independent manner.

A MIFX package is a single archive file with extension \texttt{.mifx} containing 
a canonical JSON intent definition and optional referenced artifacts.

\subsection{Purpose}

The purpose of MIFX is to reduce ambiguity and information loss in machining job exchange 
across organizational and software boundaries.

MIFX provides a stable exchange layer without altering how CAM systems program 
or how machines execute.

It separates intent from execution while preserving explicit structural relationships.

\subsection{Scope}

MIFX defines:

\begin{itemize}
\item Structured machining intent (Setups, Tools, Operations)
\item Explicit coordinate systems and transformations
\item Deterministic operation ordering
\item Artifact references via relative paths
\item Optional association to machine-neutral APT/CL toolpaths
\item Optional lightweight visualization geometry
\end{itemize}

MIFX does not define:

\begin{itemize}
\item Machine execution
\item G-code dialects
\item Simulation models
\item Digital twins
\item Controller behavior
\item Feature recognition schemas
\item CAM strategy definitions
\end{itemize}

Execution is not intent.

\subsection{Design Principles}

The specification is governed by the following principles:

\begin{enumerate}
\item \textbf{Minimal Core} --- Only what is required for portable machining intent exchange.
\item \textbf{Sequential Determinism} --- Operation order defines semantic processing order.
\item \textbf{Explicitness} --- No hidden inference or implicit relationships.
\item \textbf{Path-Based Referencing} --- All non-core artifacts are referenced by relative paths within the package.
\item \textbf{Graceful Degradation} --- Optional components SHALL NOT invalidate a conforming job.
\item \textbf{Longevity} --- Human-readable, text-based, archivally stable representation.
\item \textbf{Disk Truth} --- The archive contents are authoritative; databases MAY index but SHALL NOT redefine intent.
\item \textbf{Open Implementation} --- Unrestricted implementation of the core specification.
\end{enumerate}

\subsection{Strategic Position}

MIFX does not replace CAM systems, post processors, simulation platforms, 
or digital manufacturing suites. It defines an interoperability layer for 
structured machining intent exchange.

It may be consumed directly by standalone viewers or indexed by external systems 
(e.g., SQL databases) without altering the canonical archive structure.

\subsection{Long-Term Vision}

A MIFX document created today shall remain interpretable decades later, 
independent of vendor survival or software availability.

If JSON parsing capability and ISO APT/CL documentation remain available, 
machining intent remains reconstructible.

MIFX is designed to be minimal in scope, stable in structure, 
and independent of proprietary runtime systems.