\section{Design Principles}

The MIFX specification is defined by strict technical constraints intended to preserve clarity, portability, determinism, and neutrality.

\subsection{Single-Package Portability}

A MIFX package SHALL be distributed as a single archive file with extension \texttt{.mifx}.

All information required to interpret the core machining intent SHALL reside within that archive.

Interpretation of the core intent SHALL NOT require external services, databases, network access, or platform-specific infrastructure.

\subsection{Structural Intent Only}

MIFX represents machining intent as structured data and defines no execution semantics.

It does not define execution behavior, machine control logic, simulation models, verification procedures, inspection processes, or governance mechanisms.

\subsection{Separation of Structure and Motion}

Intent structure SHALL be defined in \texttt{job.json} and associated structured JSON documents.

Machine-neutral motion data (e.g., APT/CL) SHALL be stored as separate artifacts within the package and referenced explicitly via relative paths.

Motion data SHALL NOT be embedded within structural JSON definitions.

\subsection{Vendor and System Neutrality}

The specification SHALL NOT assume or depend upon any specific CAM system, controller, simulation platform, enterprise system, or runtime environment.

MIFX defines a data structure, not an implementation model.

\subsection{Minimal Surface Area}

The core specification SHALL include only information necessary to describe setups, operations, tools, coordinate systems, and artifact references.

Lifecycle management, revision control, inspection modeling, execution tracking, enterprise orchestration, and digital twin representations are outside the scope of MIFX.

\subsection{Path-Based Determinism}

All non-core artifacts SHALL be referenced using relative paths within the archive.

No artifact SHALL require implicit discovery rules or environment-dependent resolution.

Document structure and explicit ordering SHALL define semantic processing order.

\subsection{Archival Stability}

Core records SHALL use stable, human-readable, text-based formats (JSON).

The structure SHALL remain interpretable without proprietary software or vendor-specific infrastructure.

A conforming MIFX archive SHALL remain structurally interpretable independent of database indexing or vendor survival.