\section{Core Concepts}

This section defines the primary entities used within a MIFX package.

\subsection{Job}

A Job represents a single machining definition contained within one MIFX package.

A MIFX archive SHALL contain exactly one Job.

The Job entry point SHALL be defined in \texttt{job.json}.  
The Job document references Setups, Operations, and optional Artifacts using relative paths within the archive.

\subsection{Setup}

A Setup defines a machining coordinate context under which Operations are performed.

A Setup may represent a workholding configuration, orientation, or coordinate system.

Each Setup SHALL be defined as a separate structured JSON document within the \texttt{setup/} directory.

Setups SHALL be processed in the order referenced by \texttt{job.json}.

\subsection{Operation}

An Operation represents a machining action within a Setup.

Operations SHALL be defined as individual structured JSON documents within the \texttt{operations/} directory.

Operations SHALL be processed in the order defined by the Setup referencing them.

An Operation MAY reference:

\begin{itemize}[noitemsep]
\item a Tool definition,
\item a Toolpath Artifact,
\item optional in-process or visualization artifacts.
\end{itemize}

\subsection{Tool}

A Tool represents a machining instrument referenced by one or more Operations.

Tool structural attributes SHALL be defined in a Tool JSON document located in \texttt{geometry/tooling/}.

Operations reference Tools by identifier.

Optional visualization geometry (e.g., STL) MAY be associated with a Tool via explicit artifact reference.

\subsection{Toolpath Artifact}

A Toolpath Artifact is a machine-neutral motion file (e.g., APT, CL).

Toolpath Artifacts SHALL be stored separately from structural JSON definitions and referenced explicitly via relative paths.

Toolpath Artifacts are informational and SHALL NOT redefine structural intent.

\subsection{Geometry Artifact}

A Geometry Artifact is an optional file associated with the Job.

Geometry MAY represent:

\begin{itemize}[noitemsep]
\item setup context,
\item part representation,
\item tool visualization.
\end{itemize}

Geometry Artifacts are informational and SHALL NOT alter core semantics.

\subsection{Extension}

An Extension is an optional data block that augments a MIFX document.

Extensions SHALL be namespaced or structurally isolated from core fields.

Conforming consumers SHALL ignore unknown Extensions.

Extensions SHALL NOT redefine, override, or alter core semantics.

Core validity SHALL NOT depend upon the presence of Extensions.