\section{MIFX Job Package}

A MIFX Job Package is a single archive file with extension:

\begin{verbatim}
.mifx
\end{verbatim}

The archive SHALL be a ZIP-compatible container.

All directory names defined by this specification SHALL be treated as case-sensitive.

A conforming MIFX archive SHALL contain exactly one Job and SHALL include the following structure:

\begin{verbatim}
job.json                      (REQUIRED)

setup/                        (REQUIRED)
    setup-1.json
    setup-2.json
    ...

operations/                   (REQUIRED)
    op-1.json
    op-2.json
    ...

geometry/                     (OPTIONAL)
    setup/                    (OPTIONAL)
        setup-1.3mf
        setup-x.3mf
    tooling/                  (OPTIONAL)
        main-6.json
        main-6.stl

cldata/                       (OPTIONAL)
    op-1.apt
    op-2.apt
\end{verbatim}

\subsection{job.json}

The file \texttt{job.json} SHALL be located at the root of the archive.

It defines the normative machining intent entry point and SHALL reference:

\begin{itemize}
\item global metadata,
\item unit definition,
\item ordered Setup documents.
\end{itemize}

Only one \texttt{job.json} file SHALL exist per archive.

\subsection{setup/}

The directory \texttt{setup/} SHALL contain one JSON file per Setup.

Each Setup document SHALL define:

\begin{itemize}
\item a unique \texttt{id},
\item optional transformation matrix,
\item ordered references to Operation documents.
\end{itemize}

If a Setup is referenced in \texttt{job.json}, its JSON file SHALL exist.

\subsection{operations/}

The directory \texttt{operations/} SHALL contain one JSON file per Operation.

Each Operation SHALL define:

\begin{itemize}
\item a unique \texttt{id},
\item \texttt{setupRef},
\item optional \texttt{toolRef},
\item optional cutting conditions,
\item optional artifact references.
\end{itemize}

If an Operation is referenced by a Setup, its JSON file SHALL exist.

\subsection{geometry/}

The directory \texttt{geometry/} MAY contain optional geometry artifacts.

Subdirectories MAY include:

\begin{itemize}
\item \texttt{setup/} for part or setup geometry (e.g., 3MF, STEP)
\item \texttt{tooling/} for Tool JSON definitions and optional STL visualization
\end{itemize}

Geometry artifacts are informational and SHALL NOT affect structural semantics.

\subsection{cldata/}

The directory \texttt{cldata/} MAY contain machine-neutral motion files referenced by Operations.

If an Operation declares an artifact reference with:

\begin{verbatim}
"role": "toolpath"
\end{verbatim}

the referenced file SHALL exist at the specified relative path.

Toolpaths SHALL conform to ISO 4343 APT/CL or a documented equivalent neutral motion format.

If no toolpath artifacts are referenced, the \texttt{cldata/} directory MAY be absent.

\subsection{Path Authority}

All artifact references SHALL use explicit relative paths.

Directory inference rules SHALL NOT be used.

The \texttt{path} value within each artifact reference SHALL be authoritative.

\subsection{Extensions}

MIFX Core does not define a dedicated \texttt{extensions/} directory.

Implementation-specific files MAY be included within the archive provided that:

\begin{itemize}
\item they do not alter core semantics,
\item they are not required for structural interpretation,
\item core validity does not depend upon them.
\end{itemize}

Conforming consumers SHALL ignore unknown files without error.

\subsection{Manifest}

No manifest mechanism is defined by the MIFX Core specification.

The authoritative structure of a MIFX archive is determined solely by:

\begin{itemize}
\item the presence of \texttt{job.json},
\item valid Setup and Operation references,
\item and explicit artifact path resolution.
\end{itemize}