\section{Operation Object}

An Operation object represents a machining operation within a setup.

Operations define the machining actions performed on the workpiece and reference the resources required to execute those actions, such as toolpaths, tools, coordinate systems, and process parameters.

Each operation is stored as an independent JSON object within the \texttt{operations} directory of a setup.

Example location:

\begin{verbatim}
setups/set-1/operations/op-2.json
\end{verbatim}

\subsection{Operation Structure}

An Operation object typically contains:

\begin{itemize}
\item an operation identifier
\item a role describing the operation category
\item a kind describing the machining process
\item an optional descriptive name
\item a strategy identifier
\item artifact references to associated resources
\end{itemize}

Example:

\begin{verbatim}
{
  "id": "op-2",
  "role": "toolpath",
  "kind": "mill",
  "name": "Face1",
  "strategy": "face",

  "artifacts": [
    {
      "role": "tool",
      "kind": "json",
      "path": "../../tools/main/2.json",
      "present": true
    },
    {
      "role": "toolpath",
      "kind": "apt",
      "path": "cldata/op-2.apt",
      "present": true
    }
  ]
}
\end{verbatim}

\subsection{Operation Identifier}

Each operation must define a unique identifier using the \texttt{id} field.

Example:

\begin{verbatim}
"id": "op-2"
\end{verbatim}

The identifier allows the operation to be referenced by other objects within the package.

\subsection{Operation Role}

The \texttt{role} field describes the semantic purpose of the operation.

Typical roles may include:

\begin{itemize}
\item \texttt{toolpath}
\item \texttt{probe}
\item \texttt{manual}
\end{itemize}

The specification does not restrict operation roles to a fixed set.

\subsection{Operation Kind}

The \texttt{kind} field describes the machining process category.

Examples include:

\begin{itemize}
\item \texttt{mill}
\item \texttt{turn}
\item \texttt{wire\_edm}
\item \texttt{probe}
\end{itemize}

This value helps software systems determine how the operation should be interpreted.

\subsection{Strategy}

The \texttt{strategy} field identifies the machining strategy used by the operation.

Examples include:

\begin{itemize}
\item \texttt{face}
\item \texttt{contour}
\item \texttt{adaptive}
\item \texttt{drill}
\end{itemize}

The strategy field is informational and may vary depending on the exporting CAM system.

\subsection{Operation Artifacts}

Operations reference associated resources through artifacts.

Common artifacts associated with operations include:

\begin{itemize}
\item tool definitions
\item toolpath files
\item coordinate system definitions
\item cutting condition definitions
\item compensation definitions
\item operation offsets
\item notes or documentation
\end{itemize}

These resources are stored as separate files within the operation directory.

Software implementations may interpret only the artifacts they support while ignoring unsupported elements.