\section{Determinism and Long-Term Readability}

MIFX SHALL support deterministic interpretation and long-term archival stability.

\subsection{Sequential Semantics}

The semantic order of machining intent is defined exclusively by explicit array order within JSON documents.

\begin{itemize}
\item Setups SHALL be interpreted in the order listed in the \texttt{setups} array of \texttt{job.json}.
\item Operations SHALL be interpreted in the order referenced by each Setup.
\item No dependency graph, execution tree, or parallel structure is defined.
\end{itemize}

Reordering elements defined as sequential SHALL be considered a semantic modification.

\subsection{Explicit Referencing}

All relationships SHALL be explicit.

\begin{itemize}
\item Operations reference Setups via \texttt{setupRef}.
\item Operations reference Tools via \texttt{toolRef}.
\item External artifacts are referenced via explicit relative \texttt{path} fields.
\end{itemize}

Consumers SHALL NOT infer implicit relationships beyond those explicitly defined.

\subsection{Stable Mathematical Representation}

Coordinate transformations SHALL be represented explicitly as 4x4 matrices.

\begin{itemize}
\item Matrix storage order SHALL be declared.
\item Units SHALL be declared.
\item Coordinate convention SHALL be declared.
\end{itemize}

Transformation matrices SHALL be interpreted exactly as declared without inferred coordinate system assumptions.

No hidden orientation logic is permitted.

\subsection{Unit Declaration}

Linear units SHALL be declared in \texttt{job.json}.

All numeric values SHALL respect declared units.

Numeric values SHALL NOT be interpreted under implicit default unit systems.

\subsection{Graceful Degradation}

If optional components are missing:

\begin{itemize}
\item Missing geometry SHALL NOT invalidate the Job.
\item Missing tool visualization geometry SHALL result in default primitive rendering.
\item Missing toolpath files SHALL NOT invalidate structural parsing unless explicitly declared with \texttt{"present": true}.
\end{itemize}

MIFX readers SHALL degrade gracefully.

\subsection{Human Readability}

Core MIFX JSON documents SHALL remain:

\begin{itemize}
\item Plain UTF-8 encoded text.
\item Fully viewable and inspectable in a standard text editor.
\item Free from binary encoding.
\end{itemize}

Core documents SHALL remain readable without proprietary tooling.

\subsection{Archival Longevity}

MIFX is designed to remain interpretable independent of specific vendor software implementations.

As long as JSON parsing capability and ISO APT/CL specifications remain documented,
machining intent SHALL remain reconstructible.

\subsection{Forward Compatibility}

Extensions SHALL be represented as optional JSON fields that do not conflict with core-defined properties.

Unknown fields SHALL be ignored without failure.

Unknown artifact roles SHALL be ignored unless explicitly required by the core specification.

Core validity SHALL NOT depend upon extension-defined fields.

Future core revisions SHALL preserve backward compatibility within the same major version.