\section{Scope and Explicit Exclusions}

This section defines the functional boundaries of the MIFX specification.
The boundaries defined in this section are normative and binding.

\subsection{In Scope}

MIFX defines a portable, structured representation of machining intent, including:

\begin{itemize}[noitemsep]
    \item Job identity and metadata,
    \item ordered Setup definitions,
    \item ordered Operation definitions,
    \item Tool identity, structural attributes, and references,
    \item explicit coordinate transformations,
    \item explicit relative-path references to machine-neutral motion data (e.g., APT/CL),
    \item optional informational geometry associated with Setups or Tools,
    \item optional extension fields that do not alter core semantics.
\end{itemize}

The specification defines structure, ordering, and explicit relationships only.
It does not define execution behavior.

\subsection{Explicit Exclusions}

The following are explicitly outside the scope of MIFX:

\begin{itemize}[noitemsep]
    \item lifecycle management systems,
    \item revision control mechanisms,
    \item approval workflows,
    \item execution tracking or shop-floor feedback,
    \item inspection feature modeling,
    \item tolerance definition or GD\&T semantics,
    \item model-based definition (MBD) surface or face tagging,
    \item simulation or material removal modeling,
    \item collision detection,
    \item axis configuration or machine kinematic models,
    \item controller-specific NC dialect definition,
    \item post-processing logic,
    \item manufacturing execution systems (MES) scheduling,
    \item enterprise resource planning (ERP) integration,
    \item digital twin representations,
    \item database indexing models or hash storage strategies.
\end{itemize}

MIFX does not enforce manufacturing processes, validate machine execution,
or replace CAM systems, controllers, simulation platforms,
or enterprise orchestration systems.

MIFX defines a portable, implementation-neutral data contract
for structured machining intent exchange.