\section{Governance Model}

MIFX is an open specification intended for unrestricted implementation and exchange.

\subsection{Open Specification}

The MIFX core specification SHALL be:

\begin{itemize}
\item Publicly available
\item Freely implementable
\item Royalty-free
\item Not controlled by a commercial vendor
\end{itemize}

The specification SHALL be publicly versioned and archived.

No license SHALL restrict reading, writing, distributing, or implementing the format.

\subsection{Core Stability Principle}

The MIFX Core Data Model SHALL remain stable within a published major version.

Breaking changes SHALL NOT occur within the same major version.

New capabilities SHALL be introduced only through:

\begin{itemize}
\item Backward-compatible additions
\item Optional fields
\item Extension mechanisms
\end{itemize}

Core fields SHALL NOT be removed or redefined within a major version.

\subsection{Minimal Core Philosophy}

The MIFX core SHALL remain intentionally minimal.

The following SHALL NOT become part of the core:

\begin{itemize}
\item Machine kinematic definitions
\item Controller dialect specifications
\item Simulation engines
\item Feature recognition schemas
\item Digital twin models
\item Lifecycle or enterprise orchestration models
\end{itemize}

Additions to the core SHALL require demonstrable improvement to interoperability and portability.

If an addition increases complexity without increasing portability, it SHALL be rejected.

\subsection{Extension Mechanism}

Vendors and researchers MAY extend the format using additional JSON fields that do not conflict with core-defined properties.

Extensions:

\begin{itemize}
\item SHALL NOT modify or override core semantics.
\item SHALL NOT redefine required core fields.
\item SHALL NOT be required for structural validity.
\end{itemize}

Consumers that do not recognize an extension field SHALL ignore it without failure.

Core validity SHALL NOT depend upon extension-defined properties.

\subsection{Reference Implementations}

The specification MAY be accompanied by:

\begin{itemize}
\item A reference Viewer
\item A reference Exporter
\end{itemize}

Such implementations are illustrative only and SHALL NOT define or alter the standard.

\subsection{No Central Authority Requirement}

MIFX does not require:

\begin{itemize}
\item A certification body
\item Vendor approval
\item Formal consortium membership
\end{itemize}

Adoption is voluntary and implementation-driven.

\subsection{Versioning}

The version of a MIFX document SHALL be declared in \texttt{job.json} using the field:

\begin{verbatim}
"exportVersion": "x.y.z"
\end{verbatim}

Versioning SHALL follow the model:

\begin{itemize}
\item Major version (\texttt{x}) --- May introduce structural changes. Backward readability of prior major versions is not guaranteed.
\item Minor version (\texttt{y}) --- SHALL introduce only backward-compatible additions.
\item Patch version (\texttt{z}) --- SHALL introduce clarifications or corrections without structural change.
\end{itemize}

Documents conforming to a given major version SHALL remain readable by implementations supporting that major version.