\section{Geometry Resources}

Geometry resources represent the physical objects involved in the machining process.

These may include:

\begin{itemize}
\item part models
\item stock material
\item fixtures
\item setup assemblies
\end{itemize}

Geometry resources are stored within the \texttt{geometry} directory of the MIFX package.

Example structure:

\begin{verbatim}
geometry/
  setups/
  parts/
  stock/
  fixtures/
\end{verbatim}

The specification does not require all geometry directories to be present.

\subsection{Geometry Referencing}

Geometry resources are referenced through artifact objects contained within MIFX objects such as setups or in-process objects.

Example:

\begin{verbatim}
{
  "role": "setup_geometry",
  "kind": "3mf",
  "path": "geometry/setups/set-1.3mf",
  "present": true
}
\end{verbatim}

The \texttt{path} field references the location of the geometry file within the MIFX package.

\subsection{Supported Geometry Formats}

The MIFX specification does not mandate a single geometry format.

Common formats include:

\begin{itemize}
\item STL
\item 3MF
\item STEP
\item OBJ
\end{itemize}

Implementations may support additional formats depending on their capabilities.

\subsection{Setup Assemblies}

Setup assemblies represent the full machining configuration for a setup.

These assemblies may include:

\begin{itemize}
\item part models
\item stock material
\item fixtures
\item workholding
\end{itemize}

Assemblies are typically stored in the \texttt{geometry/setups} directory.

Example:

\begin{verbatim}
geometry/setups/set-1.3mf
\end{verbatim}

\subsection{Part Geometry}

Part models represent the design geometry of the component being manufactured.

Part geometry is typically stored in the \texttt{geometry/parts} directory.

Example:

\begin{verbatim}
geometry/parts/bracket.step
\end{verbatim}

\subsection{Stock Geometry}

Stock geometry describes the initial material from which the part will be machined.

Stock models are typically stored in the \texttt{geometry/stock} directory.

Example:

\begin{verbatim}
geometry/stock/block.stl
\end{verbatim}

\subsection{Fixture Geometry}

Fixture models represent workholding or machine fixtures used during machining.

Fixture geometry is typically stored in the \texttt{geometry/fixtures} directory.

Example:

\begin{verbatim}
geometry/fixtures/vise.step
\end{verbatim}

\subsection{Tool Geometry}

Tool geometry is not stored in the \texttt{geometry} directory.

Tool definitions, including optional geometry meshes or parametric profiles, are stored within the \texttt{tools} directory as part of the Tool object.

\subsection{In-Process Geometry}

Intermediate workpiece states are represented by In-Process objects.

Associated geometry resources are stored alongside the in-process object within the \texttt{in\_process} directory.

Example:

\begin{verbatim}
in_process/op1-5.json
in_process/op1-5.stl
\end{verbatim}